Optimal (Multiway) Spatial Joins

### 2024-06-04 msj.tex
yufei

\extraspacing \underline{\em Proof of Statement (1).} Let $\bm{t}$, $h$, and $v$ be as defined in the statement. 
Recall that $h \in \dcross_H(\bm{t})$ and $v \in \dcross_V(\bm{t})$. The segments $h$ and $v$ both cross $B_\bm{t}$, as can be verified from the definitions of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$. Thus, $h \cap v$ is a point in $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. As $r_i$ ($i \in [k-2]$) is the full rectangle of $\bm{t}[i]$, we know that $\bigcap_{i=1}^{k-2} r_i$ covers $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. Hence, point $h \cap v$ falls in $\bigcap_{i=1}^{k-2} r_i$, indicating that $h\cap v \cap \bigcap_{i = 1}^{k-2}r_i \neq \emptyset$. It follows that $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

\extraspacing \underline{\em Proof of Statement (2).} Consider the $k$-tuple $(r_1,...,r_{k-2},h,v) \in \J_1$ in statement (2). By definition of $\J_1$, segments $h$ and $v$ cross each of the rectangles $r_1,..., r_{k-2}$. By Proposition~\ref{prop:app:hv:type1:help1}, segments $h$ and $v$ must also cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. Hence, $B_\bm{t} = \bigcap_{i = 1}^{k-2}r_i'$ is non-empty as it contains the point $h \cap v$, which proves the first claim $\bm{t} = (r_1', ..., r_{k-2}') \in \J(R_1',...,R_{k-2}')$.

@@

\extraspacing \underline{\em Proof of Statement (2).} Let $r', r^*$, and $\bm{t}$ be as defined in statement (2). Let us represent $r'$ as $[x_1,x_2] \times [y_1, y_2]$. Accordingly, $r^*$ can be written as $[x_1, x_2] \times [y_1, \maxtop(r')]$.

@@

\extraspacing \underline{\em Proof of Statement (2).} Let $(r_1,...,r_{k-2},h,v)$, $h'$, and $\bm{t}$ be as defined in statement (2). Firstly, we will argue that the $(k-1)$-tuple $\bm{t}$ belongs to $\J(R_1,...,R_{k-3}, H', V)$, which is equivalent to saying that that the point $h' \cap v$ falls in all of $r_1,...,r_{k-3}$. The subsequent discussion will prove that $h' \cap v$ is in fact the same point as $h \cap v$. From $(r_1,...,r_{k-2},h,v) \in \J(R_1,...,R_{k-2},H,V)$, we already know that $h \cap v$ falls in all of $r_1,...,r_{k-2}$. Therefore, obtaining $h' \cap v = h \cap v$ will allow us to assert that $r_1,...,r_{k-3}$ all cover $h' \cap v$.

>>>>

\extraspacing \underline{\em Proof of Statement (1).} Take any $(k-2)$-tuple $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$. Let $r_i$ ($i$ $\in$  $[k-2]$) be the full rectangle of $\bm{t}[i]$. Fix any $h \in \dcross_H(\bm{t})$ and any $v \in \dcross_V(\bm{t})$. The segments $h$ and $v$ both cross $B_\bm{t}$, as can be verified from the definitions of $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$. Thus, $h \cap v$ is a point in $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. As $r_i$ ($i \in [k-2]$) is the full rectangle of $\bm{t}[i]$, we know that $\bigcap_{i=1}^{k-2} r_i$ covers $B_\bm{t} = \bigcap_{i=1}^{k-2} \bm{t}[i]$. Hence, point $h \cap v$ falls in $\bigcap_{i=1}^{k-2} r_i$, indicating that $h\cap v \cap \bigcap_{i = 1}^{k-2}r_i \neq \emptyset$. It follows that $(r_1,...,r_{k-2},h,v)$ is a result tuple in $\J(R_1,...,R_{k-2},H,V)$.

\extraspacing \underline{\em Proof of Statement (2).} Take any $k$-tuple $(r_1,...,r_{k-2},h,v) \in \J_1$. By definition of $\J_1$, segments $h$ and $v$ cross each of the rectangles $r_1,..., r_{k-2}$. By Proposition~\ref{prop:app:hv:type1:help1}, segments $h$ and $v$ must also cross each of the trimmed rectangles $r_1',..., r_{k-2}'$. Hence, $B_\bm{t} = \bigcap_{i = 1}^{k-2}r_i'$ is non-empty as it contains the point $h \cap v$, which proves the first claim $\bm{t} = (r_1', ..., r_{k-2}') \in \J(R_1',...,R_{k-2}')$.

@@

\extraspacing \underline{\em Proof of Statement (2).} Take any tuple $\bm{t} \in \J(R'_1, ..., R'_{k-2})$. Set $r' = \gbot(\bm{t})$, and let $r^*$ be the top-sliced rectangle of $r'$. If we represent $r'$ as $[x_1,x_2] \times [y_1, y_2]$, then $r^*$ can be written as $[x_1, x_2] \times [y_1, \maxtop(r')]$.

@@

\extraspacing \underline{\em Proof of Statement (2).} Take any $k$-tuple $(r_1, ..., r_{k-2}, h, v) \in \J_2$. Let $h'$ be the trimmed segment of $h$ and set $\bm{t} = (r_1, ..., r_{k-3}, h', v)$. Firstly, we will argue that the $(k-1)$-tuple $\bm{t}$ belongs to $\J(R_1,...,R_{k-3}, H', V)$, which is equivalent to saying that that the point $h' \cap v$ falls in all of $r_1,...,r_{k-3}$. The subsequent discussion will prove that $h' \cap v$ is in fact the same point as $h \cap v$. From $(r_1,...,r_{k-2},h,v) \in \J(R_1,...,R_{k-2},H,V)$, we already know that $h \cap v$ falls in all of $r_1,...,r_{k-2}$. Therefore, obtaining $h' \cap v = h \cap v$ will allow us to assert that $r_1,...,r_{k-3}$ all cover $h' \cap v$.
